\documentclass{task_description}
\usepackage[table]{xcolor}
\usepackage[bottom]{footmisc}

\newcommand{\todox}[1]{{\color{red}#1}}

\begin{document}

\thispagestyle{firstpage}
\vspace*{23mm}%
\hfill\parbox[t]{65mm}{
Herr\\
Qasim Warraich\\
Längassstrasse 54\\
3012 Bern \\[3mm]
Matrikel-Nr. 18-787-796 \\
qasim.warraich@uzh.ch\\[15mm]
\today \\
}
\vspace*{5mm}

\subsection*{Master's Thesis Specification}

\section*{``CLI Tutor''}

\subsection*{Introduction}

Despite the arguably dated appearance, difficult learning curve and practical
non-existence in the general personal computing space, Command Line Interfaces
(CLIs) have more than stood the test of time in the software development world.
There are a multitude of extremely popular tools and applications that
primarily focus on the command line as an interaction medium. Some examples
include version control software like `git', compilers and interpreters for
programming languages, package managers and various core utilities that are
popular in areas such as software development, scripting and system
administration.

As mentioned before, the use of the command line as an interaction paradigm has
effectively disappeared from a mainstream personal computer usage perspective.
This contributes greatly to the intimidation factor and learning difficulty for
those interested in getting into software engineering or system administration.
This unfamiliarity, paired with the inevitability of usage of CLIs in the
development space highlights a need to make the command line more accessible to
new users for whom text-based interaction with their computer is an alien
concept. In recent years interactive learning utilising tools such as sandboxed
environments have been gaining in popularity and have the potential to be a
suitable medium for learning command line basics through actual usage, examples
and practice.

\subsection*{The goals of this Master's thesis}
This thesis aims to determine whether an interactive learning method may ease
the introduction into command line interfaces for novice users, particularily
mitigating the `scare factor' experienced by first-time users. We do so by
creating a forgiving CLI with the goal of teaching topics such as shell
scripting basics and Unix-like core utility usage through the use of
interactive examples. We draw inspiration from the `vimtutor'
\cite{pierce_ware_smith_moolenaar_2019} utility shipping alongside the popular
terminal based text editor \emph{Vim}. The proposed tool shall allow for opt-in
analytics that are sent back to a data collection service for the purpose of
learning which mistakes are most commonly made, and to improve the tool
accordingly. To validate the tool and answer our research questions,
a user study will be conducted, most likely
with bachelor students at the University of Zurich. A secondary goal is to
embed the learning tool into a prototypical web application in order
to make it more accessible and portable.

\subsection*{Research questions}
We preliminarily define the following research questions:

\begin{itemize}
    \item Are there identifiable patterns of difficulty when it
          comes to adopting CLIs? Can the `indimidation factor' be pinned down?
    \item How should an interactive learning tool be designed to mitigate
          the difficulty and indimidation factor of learning CLIs?
    \item How can a `forgiving' shell be implemented on top of an existing
          shell to enable the transition from learning to real-world usage?
    \item Is the interactive tool more effective than text based learning methods?
    \item Are novice CLI users more likely to continue
          using CLI interfaces after using such a tool?
\end{itemize}

\subsection*{Tasks}

\paragraph{Literature review.} A look into some of the existing work performed in
this space, in order to ascertain what the core difficulties and issues that
would need to be tackled are. 

\paragraph{Outlining the curriculum.} Deciding what lessons and examples
the tutor utility should comprise. This will be done by looking at existing
learning tools, guides and through insights gained from the literature
research.

\paragraph{Development of the forgiving shell.} The task here is to
implement a CLI or TUI interface that allows for mistakes and can gently guide
the user toward a correct answer rather than producing intimidating or cryptic
errors as using a traditional shell directly might do. The `GoCui' library
might be an appropriate candidate for building a tool such as this.

\paragraph{Development of the analytics service.} The CLI tutor shall include
an opt-in feature that allows users to share their input and output logs with
an analytics service that allows us to investigate common mistakes and usage
patterns to make improvements to the tool.

\paragraph{Web tool} Embed the teaching tool into a website for demonstration
purposes and to gather more data from a broader audience.

\paragraph{Validation} Performing a user study in order to measure the
effectiveness of such a tool.

\subsection*{Milestones}

\begin{tabular}{lp{10cm}}
Deadline & What (\emph{thesis-related}) \\
\hline\noalign{\smallskip}
March 14th   & Official start of thesis. \\
March 20th  & Literature review complete. \emph{Related work section written. Research questions defined.} \\
March 24th  & First draft of curriculum completed. \\
March 29th  & Curriculum defined. \emph{Introduction and curriculum written.} \\
March 29th  & Development of tool begins. \\
April 20th  & Interaction framework completed. \\
May 10th    & Majority of lessons implemented. \\
May 25th    & Analytics service implemented. \emph{Method section mostly written.} \\
June 5th    & Web demo implemented. \\
June 15th   & Validation and study defined and begun. \\
July 10th   & Data from web users and study participants collected. \emph{Method section completed}. \\
July 20th   & Analysis of findings completed. \emph{Results and future work sections mostly completed}. \\
August 14th   & Tool, documentation \emph{and thesis} finalized. \\
September 14th & \emph{Final thesis due date}. \\
September   & Presentation including demo. \\
\end{tabular}

\subsection*{General thesis guidelines}

The typical rules of academic work must be followed. In
\cite{Bernstein2005-daguide}, Bernstein describes a number of guidelines which
must be followed. At the end of the thesis, a final report has to be
written. The report should clearly be organized, follow the usual academic
report structure, and has to be written in English using our
s.e.a.l. \LaTeX-template.

Since implementing software is also part of this thesis, state-of-the-art
design, coding, and documentation standards for the software have to be obeyed.

Effective feedback can only be provided to the student if the thesis draft is handed in well before the final deadline!

The diploma thesis has to be concluded with a final presentation for the members
of the Software Evolution and Architecture Lab (s.e.a.l.).

\subsection*{Special remarks}
\paragraph{Copyright.}
In accordance with current regulations, the student retains the copyright to his work, while providing a non-exclusive, non-revocable, time-unlimited license for it to the university. For this particular thesis, the student intends to keep all source code public so as to provide maximum accessibility to the proposed learning aid. 

\vspace{2em}
\noindent\textbf{Responsible assistant}: Dr. Carol V. Alexandru-Funakoshi

\vspace{2em}
\noindent\textbf{Signatures:}

\vspace{3\baselineskip}
\noindent Student Name\hfill Qasim Warraich
\vspace{2cm}
\bibliographystyle{abbrv}
\bibliography{proposal}

\end{document}

